\documentclass[a4paper,10pt]{article}
\usepackage[left=1in, right=1in, top=1in, bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}

\pagestyle{empty}

% Define colors
\definecolor{darkblue}{RGB}{26,13,171}
\definecolor{gray}{RGB}{128,128,128}

% Customize section headings
\titleformat{\section}{\color{darkblue}\Large\bfseries}{\thesection}{1em}{}[\titlerule]

% Customize itemize environment
\setlist[itemize]{left=0em,label=--,itemsep=0em,topsep=0em}

% Customize page margins
\geometry{top=0.75in, bottom=0.75in}

\begin{document}

% Header
\begin{center}
    \textbf{\LARGE Abdus Shakur} \\
    \vspace{5pt}
    \textbf{Senior Software Developer} \\
    \vspace{5pt}
    \textit{abdusshakurt@gmail.com | +91-814 814 8597 | } \url{https://linkedin.com/in/abdus-shakur}
\end{center}

% Professional Summary
\section*{Professional Summary}
Highly dedicated Full Stack Java Developer with over 5 years of Industry Experience in Development. Skilled in Java, Agile Methodologies, Spring Boot, API/UI Automation, React, Maven, and GIT. Excellent problem solver with good analytical skills, strong research skills, and high proficiency in devising solutions for problems.

% Work Experience
\section*{Work Experience}

\textbf{NTT DATA SERVICES, Bangalore, Karnataka, India} \hfill \textit{Dec 2021 - Present} \\
\textit{Technical Lead, Fullstack Developer} \\
\begin{itemize}
    \item Leading a team of 5 developers for Way Billing Migration Project from Legacy C Program to Message Driven Java Application.
    \item Involved in all phases of Agile, including requirement analysis, architectural design, development, testing, code review, deployment, and ongoing support for web-based application and services.
    \item Handled an IE to Chrome Browser Compatibility Project independently and took the project to completion.
\end{itemize}

\textbf{Tata Consultancy Services, Kochi, Kerala, India (TCS)} \hfill \textit{Apr 2020 - Dec 2021} \\
\textit{Micro-Services Developer – System Engineer} \\
\begin{itemize}
    \item Consistently received the highest band for three years and promoted as TCS Digital Candidate after clearing an organization-level high talent assessment in 2021.
    \item Participated in Scrum calls and development meetings to recommend system modifications and improvements.
\end{itemize}

\textit{Full Stack Developer} \hfill \textit{Sep 2019 - Dec 2021} \\
\begin{itemize}
    \item Developed defect-free and efficient code in Java 8, Spring Boot for a Multi-National Bank.
    \item Collaborated in a team-based Agile environment to accomplish objectives.
    \item Ensured proper communications are proactively triggered to the concerned audience when the regression suite fails. Conducted RCA \& sent out the details to the right audience.
\end{itemize}

\textit{Java Developer} \hfill \textit{Aug 2018 - Sep 2019} \\
\begin{itemize}
    \item Development of ERP Based application in Java. Worked on Various Modules such as Inventory, LMS, and GHR.
    \item Worked with development tools such as Rancher, Jenkins, Git, IDE (Eclipse and IDE), Postman, and Kanban Board. Experience in Testing activities, Jenkins, CI/CD Pipelines.
\end{itemize}

% Education
\section*{Education}

\textbf{Bachelor Of Engineering - Mechanical} \hfill \textit{2014 - 2018} \\
CGPA: 8.979

% Skills
\section*{Skills}
Java, SpringBoot, Selenium, PLSQL, JMeter, Git, Maven, Jenkins, RestAssured, RESTful APIs, Agile, MongoDB, Postman, Jira, GraphQL, Swagger.

% Projects
\section*{Projects}
\textbf{CSX Transportation} \hfill \textit{Duration: 2 Years} \\
\textit{Technical Lead \& Developer, Team Size: 6, Model: Agile} \\
\textit{Tools and Tech: Java, Message Driver Beans, IBM MQ, Oracle DB, PL/SQL, Docker, Sonar Cube, Kibana.} \\
Migration of Existing Mainframe Integrated C Programs into High-Performance Message Queue-driven Java Program for Processing Large Volume Waybills. Supervised programming team in developing new software applications and reviewing the code for Way Billing Services.

\textbf{US Bank} \hfill \textit{Duration: 2 Years 3 Months} \\
\textit{Full Stack Developer, Team Size: 3, Model: Agile} \\
\textit{Tools \& Tech Used: Java, Spring Boot, Maven, Git, Jenkins, Postman, Jira, GraphQL, JMETER, Docker, Sonar Cube.} \\
Involved in the development process for the conversion of Monolith Application into Microservices Based Spring Boot Application. Created APIs for Credit Score with TransUnion, Internal and External Accounts Summary, Account Details, Insights, and Customer Details for Customer Dashboard Landing Page.

\textbf{INFOR US} \hfill \textit{Duration: 1 Year 2 Months} \\
\textit{Java Development \& Testing, Team Size: 60, Model: Waterfall} \\
\textit{Tools \& Tech Used: Java, Selenium, Rest Assured, TestNG, Maven, Git, Jenkins, Jira.} \\
Created Web and API Scripts for modules such as Global HR, Learning Management System, Financials \& Supply Management, Requisition Self-service, Human Capital Management, Health-Care, Talent Management. Involved in Developing Hybrid Test Automation framework for the applications from scratch for Integrated API, UI, and Mobile for writing Automated Scripts with Java.

% Awards & Achievements
\section*{Awards \& Achievements}
\begin{itemize}
    \item Expertise with Real-time Application integrated API service automation.
    \item TCS – Received 10 Awards \& Certificates for Outstanding performance and out-of-the-box approach.
    \item TCS - Best team award based on client appreciations.
    \item TCS - On The Spot Award for Solving Critical Customer Issues.
    \item Designed an Automation framework based on Selenium, implementing a Page-Object Model, Extent Report, and query-based data extraction from Excel.
    \item Well Known in projects for out-of-the-box thinking and implementation capabilities.
\end{itemize}

% Languages
\section*{Languages}
English, Tamil, Urdu, Hindi, Malayalam.

% Footer
\begin{center} 
    \textit{Last Updated: \today}
\end{center}

\end{document}
